%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{bigfatnoob-resume}
\usepackage{graphics}


\begin{document}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     LAST UPDATED DATE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\lastupdated
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     TITLE NAME
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\profilepic{img/profile.jpg}
	\namesection{Sandeep}{Mohan}{ \urlstyle{same}\url{sandeepmohan.com} \\
		\href{mailto:sandeepmadathil@gmail.com}{sandeepmadathil@gmail.com} | 614.906.5176
	}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     COLUMN ONE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{minipage}[t]{0.33\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EDUCATION
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Education} 
		
		\subsection{Rochester Institute \\ of Technology}
		\descript{MS in Manf. \& Mech.  \\ Systems Integration}
		\location{May 2013 - Dec 2015 | Rochester, NY \\ Current. GPA: 3.89}
		\descript{Diploma in Applied Statistics}
		\sectionsep
		
		\subsection{Amrita University}
		\descript{B.Tech in Electronics Engg.}
		\location{July 2008 - May 2012 | CBE, India}
		College of Engineering \\ Cum. GPA: 3.20 
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     LINKS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Impressions} 
		LinkedIn: \href{https://www.linkedin.com/in/sandeepmohan777}{\custombold{sandeepmohan777}} \\
		Twitter: \href{https://twitter.com/msandy57}{\custombold{@msandy57}} \\
		Facebook: \href{https://www.facebook.com/sandeepmohan777}{\custombold{sandeepmohan777}}\\
		Github: \href{https://www.github.com/msandy57}{\custombold{msandy57}}
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     SKILLS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Skills}
		\location{\ibf STATISTICAL SOFTWARE}
		JMP SAS \textbullet{} Minitab \textbullet{} R \\ 
		QI Macros \textbullet{} Excel \textbullet{} SHINY \\
		\location{\ibf PROGRAMMING}
		Matlab \textbullet{} SQL \textbullet{} C++ \textbullet{} C\\
		\location{\ibf DIGITAL DESIGN}
		LabView \textbullet{} Eagle 7.0 \textbullet{} RSlogix \\
		VHDL \textbullet{} Proteus
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     COURSEWORK
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Coursework}
		\subsection{Graduate}
		Design of Experiments \\
		Statistical Quality Control\\
		Lean Six Sigma Fundamentals \\
		Manufacturing \& Mechanical Systems Fundamentals\\
		Advanced Electronics Packaging \\
		Project Management \\
		Fiber Optics Telecommunications \\
		Supply Chain and Operations Management \\
		
		
		
		\sectionsep
		
		\subsection{Undergraduate}
		Probability and Statistics\\
		Operations Research \\
		Agent Based Modelling \\
		Programmable Logic Control \\
		Process Control\\
		Optical Instrumentation\\
		
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%
		%     COLUMN TWO
		%
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
	\end{minipage} 
	\hfill
	\begin{minipage}[t]{0.66\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EXPERIENCE
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Experience}
		
		\runsubsection{GLOBALFOUNDRIES}
		\descript{| Manufacturing Excellence (Co-Op)}
		\location{Jan 2015 - Dec 2015 | Malta, NY}
		\vspace{\topsep} % Hacky fix for awkward extra vertical space
		\begin{tightemize}
			\item Worked as facilitator for deploying {\ibf Kaizen} (Continuous Improvement) events and {\ibf Root Cause Analysis} to help the {\ibf Advanced Module Engineering} modules reduce usage of test wafers in pre-production \& tool qualifications.
			\item Worked in tandem with the {\ibf Process Change Review Board} to improve the quality of statistical analysis in the submissions.
			\item Coached fellow Green Belt candidates through {\ibf DMAIC} \& {\ibf DMADV} methodologies. A qualified {\ibf Lean} \& {\ibf Six Sigma} trainer at {\ibf FAB8}.
			\item Responsible for providing statistical solutions using {\ibf JMP}. Analysis  include:  DOE, SPC, ANOVA, Linear Regression, Process Capability \& MSA.
		\end{tightemize}
		\sectionsep
		
		\runsubsection{Salicylates and Chemicals Pvt. Ltd.}
		\descript{| Engineering Intern}
		\location{August 2012 - November 2012 | Hyderabad, India}
		\begin{tightemize}
			\item Implemented {\ibf Quality at the Source} methodology using {\ibf Visual Management}.
			\item Maintenance of production schedule using {\ibf Gantt Charts}. Changes and modifications were reflected with daily updates from the production team.
			\item Assurance of quality in the raw material from suppliers.
		\end{tightemize}
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     PROJECTS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{PROJECTS}
		\runsubsection{Academic}
		\location{}
		\begin{tightemize}
			\item \href{http://sandeepmohan.com/files/DOE_Simulation.pdf}{\ibf DESIGN OF EXPERIMENTS} Identified critical factors and level settings for shrinkage in Injection Molding Process using a {\ibf 2-level Fractional Factorial design}. 
			\item \href{http://sandeepmohan.com/files/JIT_At_Diamond_Packaging.pdf}{\ibf OPERATIONS MANAGEMENT} Conducted a case study at Diamond Packaging, Rochester NY. This study analyzed and identified opportunities for improvement in their {\ibf JIT} Manufacturing System.
			\item \href{http://sandeepmohan.com/files/SigmaBrew_DMAIC.pdf}{\ibf LEAN SIX SIGMA} The project used a {\ibf DMAIC} Methodology was to achieve a high {\ibf Sigma Level} \& {\ibf ROI} for SigmaBrew - a virtual coffee shop.
			\item \href{http://sandeepmohan.com/files/SQC_Bottle_filling.pdf}{\ibf STATISTICAL QUALITY CONTROL} Analyzed the sources of variation \& proposed improvements in a Bottle Filling process using {\ibf Stewharts Control Charts} \& {\ibf Process Capability}
		\end{tightemize}
		\sectionsep
		
		\runsubsection{Industrial}
		\location{}
		\begin{tightemize}
			\item {\ibf CORPORATE STATISTICS AND DATA ANALYSIS BEST PRACTICE DOCUMENT}
			\begin{tightemize}
				\vspace{\topsep}
				\item {\ibf DFSS} project with standard reference of data analysis procedures.
				\item  Reduced inconsistencies in Process Change Review submissions by 30\%. Achieved a cost avoidance of > \$300,000.
				\item Categorized as a {\ibf BIG (Best In GLOBALFOUNDRIES)} project.
			\end{tightemize}
		\end{tightemize}
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     CERTIFICATIONS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Certification}
		\vspace{\topsep}
		\begin{tightemize}
			\item {\ibf Lean Six Sigma Green Belt} $@$ GLOBALFOUNDRIES, 2015
			\item {\ibf Advanced Certificate In Lean Six Sigma} $@$ RIT, 2015
		\end{tightemize}
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     PUBLICATIONS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Publications} 
		\begin{tabular}{p{2cm}p{9.2cm}}
			\href{http://sandeepmohan.com/files/Digital_Sphygmomanometer.pdf}{April 2012} & {\ibf Automated Digital Sphyghmomanometer} $@$ International Conference on Control Engineering - 2012\\
		\end{tabular}
		\sectionsep
		
	\end{minipage} 
\end{document}  \documentclass[]{article}
